---
title: "Communicating with Data via R Markdown"
author: "Emi Tanaka"
date: "`r Sys.Date()`"
fontfamily: bera
cc: "Mengbo Li (Organiser)"
closing: "------------------------------"
output:
  linl::linl
---

**Communicating with Data via R Markdown**

*Instructions*

1. Install the latest [R](https://cran.r-project.org/mirrors.html) (>3.5) and [RStudio Desktop](https://rstudio.com/products/rstudio/) (>1.2).
2. Install [LaTeX](https://www.latex-project.org/get/). This is rather big (e.g. MacTeX is approximate 3.9G). If you have never installed LaTeX before, then you are recommended to install via `tinytex` which is much more light-weight. Open R and enter the following commands:
```{r, eval = FALSE}
install.packages("tinytex")
tinytex::install_tinytex()
```
3. Install the following packages and its dependencies:
```{r, eval = FALSE}
install.packages(c("tidyverse", 
                 "rmarkdown", 
                 "knitr",
                 "xaringan", 
                 "usethis",
                 "rmdformats", 
                 "prettydoc",
                 "rticles",
                 "linl",
                 "shiny",
                 "bookdown",
                 "pagedown",
                 "remotes"))
# the following is not on CRAN 
remotes::install_github("gadenbuie/xaringanthemer")
remotes::install_github("hadley/emo")
```
4. Make an account at https://rstudio.cloud (it's free).
5. Make an account at https://rpubs.com (it's also free).
6. Make a github account https://github.com (yes free).
7. Install [Google Chrome browser](https://www.google.com/chrome/) on your laptop.

*Pre-Work*

You will get the most out of the workshop if you know some markdown, LaTeX, HTML/CSS and R. Please do these tutorials if you are not familiar or need to brush up with it! 

* Markdown tutorial https://www.markdowntutorial.com - 10 minutes tutorial
* LaTeX tutorial https://www.latex-tutorial.com/quick-start/
* HTML/CSS tutorial https://www.codecademy.com/learn/learn-html/modules/learn-html-elements (This is free but you need to sign up)
* Brush up in basic R (http://swirlstats.com) if you need to

*On the day*

* Bring your laptop (with administrative rights) along with your power cord.
* Registration starts at Friday 4th October 12.30pm at Carslaw Room 353, The University of Sydney.
