---
title: "Communicating with Data via R markdown"
subtitle: "\u2728 Pretty Presentations \u2728"
author: "Emi Tanaka"
email: "dr.emi.tanaka@gmail.com"
date: "4th October 2019 | COMBINE | Sydney, Australia"
pdflink: "link"
titleslide_bgimg: "images/bg3.jpg"
color_theme: "#FC427B"
output:
  xaringan::moon_reader:
    css: [ninjutsu, "assets/animate.css", "assets/cssgrid.css", "assets/custom.css", ]
    self_contained: false # if true, fonts will be stored locally
    seal: false # show a title slide with YAML information
    #yolo: false # show Karl randomly
    chakra: 'libs/remark-latest.min.js'
    beforeInit: "assets/custom.js"
    lib_dir: libs
    includes:
      in_header: "assets/custom.html"
      # before_body: 
      after_body: "assets/remarkjs_extended.html"
      # includes
    mathjax: "assets/mathjax-local/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
    nature:
      # autoplay: 100 # in milliseconds to play next slide
      # coundown: 100 # to display on each slide (TRUE if autoplay on)
      # titleSlideClass: c("center", "middle", "inverse")
      highlightStyle: dark # [arta, ascetic, dark, default, far, github, googlecode, idea, ir-black, magula, monokai, rainbow, solarized-dark, solarized-light, sunburst, tomorrow, tomorrow-night-blue, tomorrow-night-bright, tomorrow-night, tomorrow-night-eighties, vs, zenburn.]
      highlightLanguage: r # no-highlight to disable
      highlightLines: true
      highlightSpans: false # true: use `backticks` as delimiters.
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: false # disable scrolling to navigate slides
        touch: true
        click: false
      ratio: '16:9' # ['4:3', '13:9']
---



```{r titleslide, child="scripts/titleslide.Rmd"}
```

[Background photo by Adam H. Sparks]{.pos .font_small top:5px;left:5px;}

---

# HTML Slides from Rmd

::: grid

::: item 

* There are a number of ways to make html slides in Rmd including `ioslides` and `slidy`. 
* My favorite one is `xaringan` `r emo::ji("package")`!
* It's highly customisable.
* These slides are made by `xaringan`!
* Note that it uses `remark.js` to render the final html instead of `pandoc`!

:::: 

::: item 

<iframe src="https://slides.yihui.name/xaringan/" height = "450px" width = "600px"></iframe>

https://slides.yihui.name/xaringan

:::

:::

---

class: font_smaller

# `xaringan` easy slide separator `---`

::: grid 

::: item 

```markdown
---
title: "My first xaringan slide"
subtitle: "Not!"
author: "Emi Tanaka"
date: "4th October 2019"
output: 
  xaringan::moon_reader
---

# Slide after title slide

*---

# Next slide

Can use **markdown**!

```
:::

::: item

<iframe src="output/xaringan-slide-separator-demo.html"  height = "450px" width = "600px"></iframe>

:::

:::

::: { .bubble1 .pos width:300px;left:31%;top:35%;}

YAML information used for title slide

:::

::: { .bubble1 .pos width:300px;left:31%;bottom:11%;}

No spaces after <br>`---`!

:::

---

# HTML/CSS

But you want to customise more?

You do need to be a ninja to do that. 

Or know a bit about HTML/CSS.

::: grid 

::: item

HTML
```html
<div class="bg-red">
This creates a box <br>
with red background.
</div>
```



:::

::: item 

CSS
```css
.bg-red {
  background-color: red;
}

```

:::

:::

::: {.pos top:1%;left:50%; }
OUTPUT
<div class="bg-red">
This creates a box <br>
with red background.
</div>

:::


---

# HTML/CSS II

But the box and text look too squished.

I increase the padding here.

<br><br>

::: grid 

::: item

HTML
```html
<div class="bg-red">
This creates a box <br>
with red background.
</div>
```



:::

::: item 

CSS
```css
.bg-red {
   background-color: red;
*  padding: 20px;
}

```

:::

:::

::: {.pos top:1%;left:55%; }
OUTPUT
<div class="bg-red" style="padding: 20px;">
This creates a box <br>
with red background.
</div>

:::

---

# HTML/CSS III

But a white text suits better.

<br><br>

::: grid 

::: item

HTML
```html
<div class="bg-red">
This creates a box <br>
with red background.
</div>
```



:::

::: item 

CSS
```css
.bg-red {
   background-color: red;
   padding: 20px;
*  color: white;
}

```

:::

:::

::: {.pos top:1%;left:55%; }
OUTPUT
<div class="bg-red" style="padding:20px;color:white;">
This creates a box <br>
with red background.
</div>

:::

---

# HTML/CSS IV

In contrast, `span` is "inline".

<br><br>

::: grid 

::: item

HTML
```html
*<span class="bg-red">
This creates a box <br>
with red background.
*</span>
```

:::

::: item 

CSS
```css
.bg-red {
   background-color: red;
   padding: 20px;
   color: white;
}

```

:::

:::

::: {.pos top:1%;left:55%; }
OUTPUT

<span class="bg-red" style="padding:20px;color:white;">
This creates a box <br>
with red background.
</span>

:::


---

# `remark.js`: div and span classes

`remark.js` makes it easier to write `div` and `span` elements.


::: grid 

::: item bg-indigo white

Text in new line

```markdown
.bg-red[
Some text
]
```

is converted to

```markdown
<div class="bg-red">
Some text
</div>
```


::: 

::: item bg-green white 

Placing `[` `]` in the same line

```markdown
.bg-red[Some text]
```

results in 

```markdown
<span class="bg-red">
Some text
</span>
```


:::

:::

---

# `remark.js`: specify class to a whole slide



::: grid 

::: item 

<iframe class="zoom-frame" src="exercises/demo/demo-xaringan.Rmd" height="500px" width = "280px"></iframe>

::: 

::: item 

<iframe src="exercises/demo/demo-xaringan.html" height = "450px" width = "600px" "></iframe>


:::

:::



---

```{r checklist, echo = FALSE}
checklist <- c("Be able to make slides from Rmd",
               "Change the background color of a slide")
```

```{r endslide, child="scripts/endslide.Rmd"}
```
