---
title: "Challenge 7"
subtitle: "YAML"
output: 
  html_document:
    theme: spacelab
    toc: true
    toc_float: true
    df_print: "paged"
    code_folding: "hide"
    code_download: true
    number_sections: true
    
---

Change the YAML of this document to achieve the following (hint check `?rmarkdown::html_document`):

1. Add numbers to the sections.
1. A button to download the code.
1. Enable `code_folding = "hide"`.
1. Change the printing of the data frame to "kable".
1. Change the output to a pdf (you will need to comment out YAML keys that does not work with pdf). 
1. Get the tex file for previous pdf (hint `?rmarkdown::pdf_document`).
1. Change it so that the figures are pdf instead of png.




```{r setup, message = FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(fig.path = "figure/c07-")
```

# Header 1

Let's have a look at the `iris` data set. The dataset contains `r nrow(iris)` observations.

## Sub1-header 1

```{r iris-table}
iris %>% 
  group_by(Species) %>% 
  count(name = "Count") 
```



## Sub1-header 2

```{r iris-plot1}
iris %>% 
  ggplot(aes(Sepal.Length, Sepal.Width, color = Species)) + 
  geom_point() + 
  labs(title = "The iris data-set") +
  theme_bw(base_size = 18) + 
  theme(legend.position = "bottom")
```

## Sub1-header 3

```{r iris-dist}
iris %>% 
  ggplot(aes(Species, Sepal.Length)) + 
  geom_violin(aes(fill = Species)) +
  geom_boxplot(width = 0.1) + 
  theme_bw(base_size = 18) +
  guides(fill = FALSE)
```



# Header 2

Let's now have a look at `ChickWeight` data. The dataset contains `r nrow(ChickWeight)` observations and `r nlevels(ChickWeight$Chick)` chicks.

## Sub2-Header 1


```{r chick-plot, fig.height = 8}
ChickWeight %>% 
  ggplot(aes(Time, weight, color = Diet)) + 
  geom_point() +
  facet_wrap(~Chick) + 
  theme_minimal(base_size = 18)
```

## Sub2-Header 2


```{r chick-dist, fig.height = 8}
sumdat <- ChickWeight %>% 
  filter(Time == max(Time)) %>% 
  group_by(Diet) %>% 
  summarise(Median = median(weight))

ChickWeight %>% 
  filter(Time == max(Time)) %>% 
  ggplot(aes(Diet, weight)) + 
  geom_point(size = 3, alpha = 1/3) +
  theme_minimal(base_size = 18) +
  geom_point(data = sumdat, aes(Diet, Median), color = "red", size = 5)
```
