---
title: "Challenge 9"
subtitle: "R Markdown via command line"
output: rmdformats::html_clean
---

1. Find the Rmd file called `myletter.Rmd` in the `demo` folder and compile it. 
2. Collect and make note of the names of your fellow workshop participants.
3. The following people are a data frame of workshop particpants. Add/replace your the particpant data with your name and people you met in this workshop. 

```{r participants, message = FALSE}
library(tidyverse)
dat <- tribble(~first_name, ~last_name,
               "Will", "Smith",
               "Jada", "Pinkett",
               "Jaden", "Smith",
               "Willow", "Smith",
               "Homer", "Simpson",
               "Marge", "Simpson",
               "Bart", "Simpson",
               "Lisa", "Simpson",
               "Maggie", "Simpson"
               )
dat
```

4. I want to replace the generic letter with a personalised letter by changing "Workshop Participant" replaced with their name and "Dear Participant" replaced with "Dear [their first name]". Manually changing the names is a lot of work. The following code implements a programmatic way of generating the letters but you need to modify `myletter.Rmd` YAML with parameters `first_name` and `last_name`. Can you modify `myletter.Rmd` to generate the personalised letters? 

```{r, eval = FALSE}
for(i in 1:nrow(dat)) {
  first_name <- dat$first_name[i]
  last_name <- dat$last_name[i]
  output_file <- paste0("myletter_", first_name, last_name)
  rmarkdown::render("exercises/demo/myletter.Rmd", 
                    params = list(first_name = first_name,
                                  last_name = last_name),
                    output_file = output_file)
}
```

5. (As an additional challenge, you may try to replace the for loop with `purrr::walk2` if you are familiar with functional programming).

